Spectral Lags in Very High Energy Emission of Gamma Ray Bursts

### 2013-11-23 gammaRays.tex
Partially drafted Very high energy bursts fraction section

>>>>

Our final test is to calculate how much of the observable bursts can be observed in the very high energy range -- GeV and above.

To do so, we need to compute the number of bursts visible in a given energy range, which is the integral over space and jet directions:
\begin{align}
b\left(\omega_1,\omega_2\right) &= \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} 2\pi \sin\chi \dif\chi \nonumber\\
&\approx 2\pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} \chi \dif\chi = \pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_2\right)
\end{align}
Here $z_\text{max}\left(\omega_1,\omega_2\right)$ and $\chi_\text{max}\left(z,\omega_1,\omega_2\right)$ are the same values we used in the previous sections: the maximum redshift from which a burst can be observed, and the maximum off-axis angle with which the burst at redshift $z$ can be observed.

The fraction in question is simply the ratio of these:
\begin{equation}
f\left(\omega_1,\omega_2,\omega_3\right) = \frac{b\left(\omega_2,\omega_3\right)}{b\left(\omega_1,\omega_3\right)} = \frac{\int_0^{z_\text{max}\left(\omega_2,\omega_3\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_2,\omega_3\right)}{\int_0^{z_\text{max}\left(\omega_1,\omega_3\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_3\right)}
\end{equation}

The ratio for our set of parameters is $f_m \approx 0.072$. The ratio computed from observations is $f_o = ...$. The binary distribution gives us the probability for it to happen:
\begin{equation}
...
\end{equation}
which means that the model fits observations in this test.
